\documentclass[letterpaper,10pt]{article}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{enumitem}
\setlist{nolistsep}

\begin{document}

\begin{center}
\textbf{\Huge RAHUL PRAKASH SHELKE}
\end{center}
\begin{center}
LinkedIn | GitHub | Mobile: +91-9130619363 | Email: rahulshelke981@gmail.com
\end{center}

% Technical Skills
\noindent\textbf{\underline{TECHNICAL SKILLS}}
\begin{itemize}
\item Programming Languages: Python, C, SQL, HTML, CSS
\item Tools: Tensorflow, Pytorch, Dash, Docker, Git, AWS, MySQL, MongoDB, Cassandra, Tableau, PowerBI
\item Technologies: Machine Learning, Deep Learning, NLP, CV, Data Structures and Algorithms
\end{itemize}

% Work Experience
\noindent\textbf{\underline{WORK EXPERIENCE}}

\noindent\textbf{Altimetrik}
\begin{itemize}
\item \textbf{Associate Data Scientist} \hfill Jun 2022 – Jan 2023 \\
Bengaluru, Karnataka
    \begin{itemize}
    \item Enhanced NLP-based product functionality with an intent classifier using RASA.
    \item Developed Transformer models for emotion classification and sarcasm detection, achieving F1 scores exceeding 80% using AWS EC2 with GPU support and Docker for efficient containerization.
    \item Implemented trend analysis models for NLP products, utilizing LDA and time series modeling for accurate forecasting.
    \end{itemize}
\item \textbf{Project Intern} \hfill Jan 2022 – Jun 2022 \\
Bengaluru, Karnataka
    \begin{itemize}
    \item Explored operational challenges, translating them into data science problem statements.
    \item Created interactive dashboards with Flask and Plotly for comprehensive data visualization.
    \item Led a Proof of Concept (POC) initiative on intent classification for NLP products.
    \end{itemize}
\end{itemize}

\noindent\textbf{Railofy – Rodeo Travel Technologies}
\begin{itemize}
\item \textbf{Data Science Intern} \hfill Aug 2021 – Nov 2021 \\
Mumbai, Maharashtra
    \begin{itemize}
    \item Managed projects using ElasticSearch and MySQL for efficient data management.
    \item Designed a model performance dashboard with Kibana for real-time monitoring and analysis.
    \item Ensured model accuracy by monitoring data drift and target drift.
    \end{itemize}
\end{itemize}

\noindent\textbf{Madras Scientific Research Foundation}
\begin{itemize}
\item \textbf{Content Development Intern} \hfill Jul 2021 – Sep 2021 \\
Tamil Nadu, Chennai
    \begin{itemize}
    \item Authored AI/ML blog posts covering tools like OpenCV, DyNet, and technologies like NER.
    \end{itemize}
\end{itemize}

% Education
\noindent\textbf{\underline{EDUCATION}}
\begin{itemize}
\item \textbf{University of Mumbai} \\
Bachelors of Engineering - Computer Science and Engineering \hfill Aug 2016 – Nov 2020 \\
CGPA: 7.32/10
\end{itemize}

% Projects
\noindent\textbf{\underline{PROJECTS}}
\begin{itemize}
\item \textbf{HR Analytics} – Conducted EDA and applied machine learning for classification using pandas, numpy, matplotlib, and sklearn.
\item \textbf{Web Scraping Data \& Data Visualization} – Extracted financial data from Yahoo! Finance with BeautifulSoup and performed exploratory data analysis.
\end{itemize}

\end{document}
